BSTERGM: Bayesian Separable-Temporal Exponential family Graph Models

### 2020-12-10 doc/doc.tex
tex 1211_0230

% \begin{figure}
%     \begin{center}
%     \includegraphics[scale=0.5]{LS_ggplot_2.png}
%     \caption{Latent positions of politicians and bills.}
%     \label{fig:ls}
%     \end{center}
% \end{figure}

@@

I use the ordinary normal prior $p(\theta^+)\sim\mathcal{N}(0,100)$ and $p(\theta^-)\sim\mathcal{N}(0,100)$,
and set the proposal distribution of main chain $\epsilon\sim\mathcal{N}(0,0.0004)$.
The auxiliary chains consist of 1000 iterations and the main chain consists of 50000 iteration.
In this setting, the BSTERGM fitting algorithm run 250 iteration of main chain per a minute on the intel i7-8700(3.20GHz) CPU.

After generating the chain, I cut first 10000 samples for a burn-in period and thin the sample by 10.
The posterior estimates for each network and histograms are follows.
%mean, sd
%hist

For the diagnostics, I attach traceplots and autocorrelation plots.
%traceplot
%acf

In addition, here are traceplots of the number of edges in last auxiliary chain.
They shows that all chains are not degenerated at last parameter point.
%lastsampler

Finally, I append the results of goodness of fit.
%GOF table

>>>>

\begin{figure}[h]
    \begin{center}
    \includegraphics[scale=0.23]{pictures/m1_19_nework.png}
    \includegraphics[scale=0.23]{pictures/w1_19_nework.png}
    \includegraphics[scale=0.23]{pictures/f1_19_nework.png}
    \caption{Sequence 1}
    % \label{fig:ls}
    \end{center}
\end{figure}
\begin{figure}[h]
    \begin{center}
    \includegraphics[scale=0.23]{pictures/m2_19_nework.png}
    \includegraphics[scale=0.23]{pictures/w2_19_nework.png}
    \includegraphics[scale=0.23]{pictures/f2_19_nework.png}
    \caption{Sequence 2}
    % \label{fig:ls}
    \end{center}
\end{figure}
\begin{figure}[h]
    \begin{center}
    \includegraphics[scale=0.23]{pictures/m3_19_nework.png}
    \includegraphics[scale=0.23]{pictures/w3_19_nework.png}
    \includegraphics[scale=0.23]{pictures/f3_19_nework.png}
    \caption{Sequence 3}
    % \label{fig:ls}
    \end{center}
\end{figure}
\clearpage

@@

I use the ordinary normal prior $p(\theta^+)\sim\mathcal{N}(0,100)$ and $p(\theta^-)\sim\mathcal{N}(0,100)$,
and set the proposal distribution of main chain $\epsilon\sim\mathcal{N}(0,0.0004)$.
The auxiliary chains consist of 1000 iterations and the main chain consists of 50000 iteration.
In this setting, the BSTERGM fitting algorithm run 2400 iterations of main chain per a minute on the intel i7-8700(3.20GHz) CPU.

After generating the chain, I cut first 10000 samples for a burn-in period and thin the sample by 10.
The posterior estimates for each network and histograms are follows.
%mean, sd
\begin{table}[h!]
    \centering
        \begin{tabular}{c | c | c | c }
            Sequence & Parameter & Estimate & Std.Error \\
            \hline \hline
            1 & $\theta^+$ & -2.336387 & 0.1274921 \\
            1 & $\theta^-$ & 1.043077 & 0.1722938 \\
            2 & $\theta^+$ & -1.435648 & 0.1009999 \\
            2 & $\theta^-$ & 0.9332358 & 0.1358161 \\
            3 & $\theta^+$ & -5.02916 & 0.2097569 \\
            3 & $\theta^-$ & 2.225616 & 0.1904817 \\
        \end{tabular}
        \caption{Fitted parameters summary}
        % \label{tab:data}
    \end{table}
\clearpage
%hist
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.23]{pictures/net1seq_chain1_BSTERGM_formation_histogram.png}
        \includegraphics[scale=0.23]{pictures/net1seq_chain1_BSTERGM_dissolution_histogram.png}
    \caption{Sequence 1, left: formation, right: dissolution}
    % \label{fig:ls}
    \end{center}
\end{figure}

\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.23]{pictures/net2seq_chain1_BSTERGM_formation_histogram.png}
        \includegraphics[scale=0.23]{pictures/net2seq_chain1_BSTERGM_dissolution_histogram.png}
    \caption{Sequence 2, left: formation, right: dissolution}
    % \label{fig:ls}
    \end{center}
\end{figure}

\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.23]{pictures/net3seq_chain1_BSTERGM_formation_histogram.png}
        \includegraphics[scale=0.23]{pictures/net3seq_chain1_BSTERGM_dissolution_histogram.png}
    \caption{Sequence 3, left: formation, right: dissolution}
    % \label{fig:ls}
    \end{center}
\end{figure}
\clearpage

For the diagnostics, I attach traceplots and autocorrelation plots.
The autocorrelation of each chain decrease rapidly as lag increases.
Moreover, traceplots shows that the MCMC samples are mixed well.
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.23]{pictures/net1seq_chain1_BSTERGM_formation_traceplot.png}
        \includegraphics[scale=0.23]{pictures/net1seq_chain1_BSTERGM_dissolution_traceplot.png} \\
        \includegraphics[scale=0.23]{pictures/net1seq_chain1_BSTERGM_formation_acf.png}
        \includegraphics[scale=0.23]{pictures/net1seq_chain1_BSTERGM_dissolution_acf.png}
    \caption{Sequence 1, left: formation, right: dissolution}
    % \label{fig:ls}
    \end{center}
\end{figure}
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.23]{pictures/net2seq_chain1_BSTERGM_formation_traceplot.png}
        \includegraphics[scale=0.23]{pictures/net2seq_chain1_BSTERGM_dissolution_traceplot.png} \\
        \includegraphics[scale=0.23]{pictures/net2seq_chain1_BSTERGM_formation_acf.png}
        \includegraphics[scale=0.23]{pictures/net2seq_chain1_BSTERGM_dissolution_acf.png}
    \caption{Sequence 2, left: formation, right: dissolution}
    % \label{fig:ls}
    \end{center}
\end{figure}
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.23]{pictures/net3seq_chain1_BSTERGM_formation_traceplot.png}
        \includegraphics[scale=0.23]{pictures/net3seq_chain1_BSTERGM_dissolution_traceplot.png} \\
        \includegraphics[scale=0.23]{pictures/net3seq_chain1_BSTERGM_formation_acf.png}
        \includegraphics[scale=0.23]{pictures/net3seq_chain1_BSTERGM_dissolution_acf.png}
    \caption{Sequence 3, left: formation, right: dissolution}
    % \label{fig:ls}
    \end{center}
\end{figure}
\clearpage
In addition, as a procedure of diagnostics for auxiliary chains,
here are traceplots of the number of edges in last auxiliary chain.
They shows that all chains are not degenerated at last parameter point during the iterations of auxiliary chain.

%lastsampler
\begin{figure}[h]
    \begin{center}
        \includegraphics[scale=0.23]{pictures/net1seq_chain1_lastsampler_num_edges.png}
        \includegraphics[scale=0.23]{pictures/net2seq_chain1_lastsampler_num_edges.png}
        \includegraphics[scale=0.23]{pictures/net3seq_chain1_lastsampler_num_edges.png}
    \caption{Sequence 1, left: formation, right: dissolution}
    % \label{fig:ls}
    \end{center}
\end{figure}
\clearpage

Finally, I append the results of goodness of fit.

%GOF table
